---
title: "Classification Model for Spam Emails"
author: "Tiina Vaahtio"
date: "6/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Project Introduction:
In this project we want to build a predictive model to recognize spam email. 

The dataset is from https://vincentarelbundock.github.io/Rdatasets/datasets.html and it contains 4601 emails from which 1813 were identified as spam. 


## Data Preparation 

Preview of the data:

```{r echo=FALSE}
spam <- read.csv("/cloud/project/spam7.csv")

head(spam)

```


Summary Statistics: 

```{r echo=FALSE}

summary(spam)

```

Renaming and Transforming columns: 

- Rename column name crl.tot 

```{r}
names(spam)[names(spam)=="crl.tot"]<-"lencap"
```

- Transform yesno column to 0, 1:
```{r echo=FALSE}
library(car)
```


```{r}
spam$yesno<-recode(spam$yesno, "'y'=1; 'n'=0") 

```
## Build and Train Model 

-Create training and test datasets 

```{r echo=FALSE}
library(caTools)
```


```{r}
split<-sample.split(spam, SplitRatio = 0.8)
train<-subset(spam, split=="TRUE")
test<-subset(spam, split=="FALSE")
```

-Fit model 
```{r}
email_model<- glm(yesno ~ lencap+dollar+bang+money+n000+make, data = train, family= "binomial")

summary(email_model)
```
- Create Predictions for Test Data
```{r}
res<-predict(email_model, test, type="response")

```


```{r echo=FALSE}
confmatrix<-table(Actual_value=test$yesno, Predicted_value= res>0.5)
confmatrix
```

- Accuracy Score
```{r echo=FALSE}
print((confmatrix[[1,1]]+confmatrix[[2,2]])/ sum(confmatrix))
```
-ROC plot
```{r echo=FALSE}
library(pROC)
roc(test$yesno, res, plot=TRUE, legacy.axes=TRUE, percent=TRUE, xlab="False Positive Percentage", ylab="True Postive Percentage", col="#377eb8", lwd=4, print.auc=TRUE)
```

